Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-19 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

To address this problem, we are going to consider a simple rule which
can induce well-behaved QIVPMs by quantum probability measures systematically.
When we generalized quantum probability measures to QIVPMs, we changed
the range from the unit interval~$\left[0,1\right]$ to a set of
intervals~$\mathscr{I}$. This replacement suggests to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
to replace a real-valued probability~$\mu\left(P\right)$ by an interval-valued
one~$\iota\left(\mu\left(P\right)\right)$. In other words, compositing
$\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
produces a function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
which has the same domain and range as a QIVPM. In order to guarantee
$\iota\circ\mu$ always a QIVPM, we consider the following homomorphism-like
properties for $\iota$.

@@

In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
there is always a state consistent with the composited QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{B}}$~\citep{HOSTunpublished}.
Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower. To state this result, we introduce a few technical notions.
First, the norm of a pure state~$\ket{\psi}$ is defined as usual
$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Then, the norm
of the difference of two states~$\rho$ and $\rho'$ is just the
usual operator norm
\begin{equation}
\left\Vert \rho-\rho'\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert \left(\rho-\rho'\right)\ket{\psi}\right\Vert \,,
\end{equation}
which is also commonly known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.

@@

Although THOS rules have many desirable properties, the intervals
it mapping to either is trivial or contains infinity intervals.

@@

Since $\iota$ maps to intervals, we can decompose it into two functions:
its left-end and right-end $\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992}.
It is well-known that a Wright-convex function is midpoint-convex
or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
i.e., we have
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
\end{equation}
Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
the left-end function~$\iotal$ must be continuous on the unit open
interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
Therefore, either $\iota$ maps every number to the same interval,
or the number of intervals that $\iota$ maps to must be uncountable.

>>>>

To address this problem, we are going to introduce a simple rule which
can induce well-behaved QIVPMs by quantum probability measures systematically.
When we generalized quantum probability measures to QIVPMs, we changed
the range from the unit interval~$\left[0,1\right]$ to a set of
intervals~$\mathscr{I}$. This replacement suggests to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
to replace a real-valued probability~$\mu\left(P\right)$ by an interval-valued
one~$\iota\left(\mu\left(P\right)\right)$. In other words, compositing
$\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
produces a function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
which has the same domain and range as a QIVPM. In order to guarantee
$\iota\circ\mu$ always a QIVPM, we consider the following homomorphism-like
properties for $\iota$.

@@

In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
there is always a state consistent with the composited QIVPM~$\iota\circ\mu_{\rho}^{\mathrm{B}}$~\citep{HOSTunpublished}.
Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower. To state this result, we introduce a few technical notions.
First, the norm of a pure state~$\ket{\psi}$ is defined as usual
$\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Then, the norm
of the difference between two states~$\rho$ and $\rho'$ is just
the usual operator norm
\begin{equation}
\left\Vert \rho-\rho'\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert \left(\rho-\rho'\right)\ket{\psi}\right\Vert \,,
\end{equation}
which is also commonly known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.

@@

Although a THOS rule have many desirable properties, the set of intervals
it mapping to either is trivial or contains infinite intervals.

@@

Since $\iota$ maps to intervals, we can decompose it into two functions:
its left-end and right-end $\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992}.
It is well-known that a Wright-convex function is midpoint-convex
or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
i.e., we have
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
\end{equation}
Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
the left-end function~$\iotal$ must be continuous on the unit open
interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
Therefore, either $\iota$ maps every number in $\left(0,1\right)$
to the same interval, or the number of intervals that $\iota$ maps
to must be uncountable.
